Expected Dependency Pair Match: Predicting translation quality with expected syntactic structure

### 2009-08-11 mtjournal.tex
repaired description of T features

The experiments here leverage the TERp optimizer but extend
the set of subscores by including the syntactic and n-gram overlap
features (modified to reflect false and missed detection rates for the TERp
format rather than precision and recall). The subscores explored include:
\begin{description}
\item[E]: the 8 fully syntactic subscores from the EDPM family, including
  false/miss error rates for the $dl$, $lh$, $dlh$, and $dh$ decompositions. 
\item[N]: the 4 n-gram subscores from the DPM family;
  specifically, error rates for the $1g$ and $2g$ decompositions.
\item[T]: the 11 subscores from TERp, which include matches, insertions, deletions, substitutions, shifts, and
  synonym and stem matches, edit distances between paraphrases, and the. 
\end{description}

>>>>

The experiments here leverage the TERp optimizer but extend
the set of subscores by including the syntactic and n-gram overlap
features (modified to reflect false and missed detection rates for the TERp
format rather than precision and recall). The subscores explored include:
\begin{description}
\item[E]: the 8 fully syntactic subscores from the EDPM family, including
  false/miss error rates for the $dl$, $lh$, $dlh$, and $dh$ decompositions. 
\item[N]: the 4 n-gram subscores from the DPM family;
  specifically, error rates for the $1g$ and $2g$ decompositions.
\item[T]: the 11 subscores from TERp, which include matches, insertions, deletions, substitutions, shifts,
  synonym and stem matches, and four paraphrase edit scores.
\end{description}
